An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-05-01 VLDB2026/main.tex
Update main.tex

	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015} , covering a diverse range of domains. We independently generate attribute for each dataset.
	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.
	\textcolor{red}{In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.}

@@

	\textit{Multi-Thread Search.}
	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
	%Puck performs well on large-scale datasets, but its performance degrades on small datasets. Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets. 
	\textcolor{blue}{Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization. }
	CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets. The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity. Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.

@@

	\textcolor{blue}{
		In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.
		%In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95). This shows that the design of current algorithms still needs improvement. We suggest that future range filtering algorithms should include Faiss as a baseline.
	}

>>>>

	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains. We independently generate attribute for each dataset.
	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.
	\textcolor{red}{In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.}

@@

	\textit{Multi-Thread Search.}
	As shown in Figure~\ref{fig:exp_1_2_SingleLabel_16thread}, UNG continues to achieve the best performance. 
	%Puck performs well on large-scale datasets, but its performance degrades on small datasets. Puck is tailored for large-scale scenarios, and optimizations such as two-level inverted indexing and hierarchical quantization introduce unnecessary overhead on small datasets. 
	Puck performs well on large datasets but degrades on smaller ones due to overhead from optimizations like two-level inverted indexing and hierarchical quantization. CAPS maintains a relatively high throughput under multi-threads but exhibits limited adaptability to different datasets. The vector distribution of the dataset affects the construction of its \textcolor{blue}{partitioned index.}
	 ACORN performs poorly overall, primarily due to the sensitivity of its hyperparameter $\gamma$ to attribute selectivity. Without careful tuning based on dataset characteristics, it is challenging to construct an effective index.

@@

		In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.
		%In our experiments, we find that many range filtering algorithms perform worse than Faiss at high recall (0.95). This shows that the design of current algorithms still needs improvement. We suggest that future range filtering algorithms should include Faiss as a baseline.
